### 2018-07-13 doc/plos/text/manuscript.tex
add all_nowcasts figure and caption

\begin{figure}[!h]
  \maybeincludegraphics{sensor_heatmap}
  \caption{
    {\bf National sensor readings fitted from eight data sources.}
    Top: Plot of sensor readings and ground truth wILI (black) over time,
    highlighting sensor noise.
    Bottom: Heatmap of sensor readings over time, highlighting sensor
    intermittency.
  }
  \label{figure_sensor_heatmap}
\end{figure}

@@

In total, we produced 29,103 nowcasts for 75 US locations across 397 weeks
spanning 2010w45--2018w24. Locations include the US as a whole, the 10 HHS
regions, the 9 census divisions, the 50 states, the District of Columbia,
Puerto Rico, the US Virgin Islands, New York City, and New York state
\textit{excluding} New York City. Although these were computed in retrospect,
models were trained using only data that would have been available at the time.
Namely, whenever possible, preliminary values of wILI were used in place of
final values.

>>>>

\begin{figure}[!ht]
  \maybeincludegraphics{sensor_heatmap}
  \caption{
    {\bf National sensor readings fitted from eight data sources.}
    Top: Plot of sensor readings (colors) and ground truth wILI (black) over
    time, highlighting sensor noise.
    Bottom: Heatmap of sensor readings over time, highlighting sensor
    intermittency.
  }
  \label{figure_sensor_heatmap}
\end{figure}

@@

In total, we produced 29,103 nowcasts for 75 US locations across 397 weeks
spanning 2010w45--2018w24. Locations include the US as a whole, the 10 HHS
regions, the 9 census divisions, the 50 states, the District of Columbia,
Puerto Rico, the US Virgin Islands, New York City, and New York state
\textit{excluding} New York City. Fig~\ref{figure_all_nowcasts} shows a
time-series comparison of all nowcasts with ground truth. Although these
nowcasts were computed in retrospect, models were trained using only data that
would have been available at the time. Namely, whenever possible, preliminary
values of wILI were used in place of final values.

\begin{figure}[!ht]
  \maybeincludegraphics{all_nowcasts}
  \caption{
    {\bf Nowcasts compared with ground truth.}
    Each subpanel contains a plot of nowcast (color) and ground truth (black)
    in a particular location within the US. All subplots share the same scale
    in both time and magnitude.
  }
  \label{figure_all_nowcasts}
\end{figure}
